Stat 400 Project

### 2021-12-07 Stat 400 proj.Rmd
print removed

      #incubation time code
      infected_people <- new_status[new_status[,3] == 'I',]
      new_inc_time <- as.numeric(infected_people[,4]) - 1
      infected_people[,4] <- new_inc_time
      other_people <- new_status[new_status[,3] != 'I',]
      new_status <- rbind(infected_people, other_people)
      print(infected_people)

>>>>

      #incubation time code
      infected_people <- new_status[new_status[,3] == 'I',]
      new_inc_time <- as.numeric(infected_people[,4]) - 1
      infected_people[,4] <- new_inc_time
      other_people <- new_status[new_status[,3] != 'I',]
      new_status <- rbind(infected_people, other_people)
